\documentclass[12pt,a4paper]{ctexart}

\usepackage{geometry}
\geometry{left=2.7cm,right=2.7cm,top=2.54cm,bottom=2.54cm}
\usepackage{setspace}
\setstretch{1.25}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{amsmath,amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{bookmark}
\usepackage[backend=biber,style=gb7714-2015,sorting=none]{biblatex}

\addbibresource{refs/review.bib}

\setcounter{tocdepth}{3}
\setcounter{secnumdepth}{3}

\ctexset{
  section = {
    name = {第,章},
    number = \chinese{section},
    format = \centering\heiti\zihao{3},
    beforeskip = 24pt,
    afterskip = 12pt
  },
  subsection = {
    format = \heiti\zihao{4},
    beforeskip = 24pt,
    afterskip = 12pt
  },
  subsubsection = {
    format = \heiti\zihao{-4},
    beforeskip = 12pt,
    afterskip = 12pt
  }
}

\title{面向多视图几何重建的学习方法综述：以 VGG 团队为例}
\author{}
\date{}

\begin{document}

\begin{titlepage}
  \centering
  {\heiti\zihao{3}《文献检索与论文写作》\par}
  \vspace{0.8cm}
  {\heiti\zihao{3}课程报告\par}
  \vspace{2.2cm}
  {\heiti\zihao{3}面向多视图几何重建的学习方法综述：\par}
  \vspace{0.2cm}
  {\heiti\zihao{3}以 VGG 团队为例\par}
  \vspace{2.4cm}
  \begin{flushleft}
    {\songti\zihao{4}组\quad 长：\underline{\hspace{8.5cm}}\par}
    \vspace{0.6cm}
    {\songti\zihao{4}组\quad 员：\underline{\hspace{8.5cm}}\par}
    \vspace{0.6cm}
    {\songti\zihao{4}专\quad 业：\underline{\hspace{8.5cm}}\par}
    \vspace{0.6cm}
    {\songti\zihao{4}班\quad 级：\underline{\hspace{8.5cm}}\par}
    \vspace{0.6cm}
    {\songti\zihao{4}提交日期：\underline{\hspace{7.8cm}}\par}
  \end{flushleft}
  \vfill
\end{titlepage}

\clearpage
\section*{摘要}
\addcontentsline{toc}{section}{摘要}
本文围绕多视图几何重建中的学习方法展开综述，聚焦 Oxford Visual Geometry Group（VGG）团队近五年的代表工作，分析该方向如何从传统结构恢复管线逐步演化到端到端学习、可微结构恢复以及统一前馈式几何预测框架。全文首先梳理传统 SfM/MVS 的任务定义与关键瓶颈，再从几何先验注入、对应关系学习、可微优化和统一几何表示四个层面总结 VGG 团队的研究主线，并结合 CoTracker、VGGSfM、VGGT 等代表性成果讨论学习方法对多视图几何重建范式的推动作用。最后，本文从鲁棒性、效率、统一性与可扩展性等角度，对该研究体系的特点、局限与未来趋势进行综合评述。

\par\noindent\textbf{关键词：}多视图几何重建，Structure-from-Motion，视觉几何，对应学习，VGG

\clearpage
\section*{ENGLISH DISSERTATION TITLE}
\addcontentsline{toc}{section}{ABSTRACT}
\begin{center}
  {\bfseries\zihao{3} LEARNING METHODS FOR MULTI-VIEW GEOMETRIC RECONSTRUCTION: A REVIEW WITH THE VGG TEAM AS A CASE STUDY}
\end{center}

\section*{ABSTRACT}
This report reviews recent learning-based methods for multi-view geometric reconstruction, with a focus on the Oxford Visual Geometry Group (VGG) and its representative works over the last five years. We first revisit the classical SfM/MVS pipeline and its limitations in correspondence estimation, global consistency, and optimization efficiency. We then organize the VGG research line into four connected themes: geometric priors, correspondence learning, differentiable structure from motion, and feed-forward geometric prediction. Representative works such as CoTracker, VGGSfM, and VGGT are discussed to show how learning-based methods have progressively redefined the traditional multi-view geometry pipeline. Finally, we summarize the main characteristics, current limitations, and future opportunities of this research line.

\par\noindent\textbf{KEY WORDS:} multi-view geometry, structure from motion, visual geometry, correspondence learning, VGG

\clearpage
\tableofcontents

\clearpage
\input{sections/01_intro}
\clearpage
\input{sections/02_background}
\clearpage
\input{sections/03_correspondence}
\clearpage
\input{sections/04_differentiable_sfm}
\clearpage
\input{sections/05_feedforward_geometry}
\clearpage
\input{sections/06_conclusion}

\clearpage
\printbibliography[title={参考文献}]

\end{document}
